DeepSphere: a graph-based spherical CNN

### 2019-09-25 main.tex
Updates from Overleaf

We start by proving that for smooth functions, the sum converges toward an integral as the sampling increase in size.
\begin{prop}\label{prop:1}
	For an equal area sampling $\{x_i\in\S^2\}_{i=0}^{n-1}: A_i=A_j \forall i,j$ of the sphere it is true that for all $f: \S^2 \rightarrow \R$ Lipschitz with respect to the Euclidean distance $\|\cdot\|$ with Lipschitz constant $C_f$
	\begin{equation*}
	\left| \int_{\S^2}f({ x})\text{d}{\mu(x)} - \frac{1}{n}\sum_i f( x_i)\right|\leq \mathcal L_fd^{(n)}.	    
	\end{equation*}
	Furthermore, for all $y\in\S^2$ the Heat Kernel Graph Laplacian operator $L^t_n$ converges pointwise to the functional approximation of the Laplace Beltrami operator $L^t$
	\begin{equation*}
	 L_n^tf(y)\xrightarrow{n\to\infty} L^tf(y).
	\end{equation*}
\end{prop}
\begin{proof}
\nati{@martino, the function should be from $\S^2$ instead of $\R^3$ here right? }
	Assuming $f:\R^3\rightarrow \R$ is Lipschitz with Lipschitz constant $C_f$, we have
	\begin{equation*}
	\left| \int_{\sigma_{i}}f({ x})\text{d}{\mu(x)} - \frac{1}{n}f( x_i)\right| \leq C_fd^{(n)}\frac{1}{n},	    
	\end{equation*}
	where $\sigma_i\in \S^2$ is the subset of the sphere corresponding to the patch arround $x_i$. Remember that the sampling is equal area.
	Hence, using the triangular inequality and summing all the contributions of the $n$ patches, we obtain
	\begin{equation*}
	\left| \int_{\S^2}f({ x})\text{d}{\mu(x)} - \frac{1}{n}\sum_i f( x_i)\right| \leq \sum_i \left| \frac{1}{4\pi^2} \int_{\sigma_{i}}f({ x})\text{d}{\mu(x)} - \frac{1}{n}f( x_i)\right|\leq n  C_fd^{(n)}\frac{1}{n} = C_fd^{(n)}
	\end{equation*}
	A direct application of this result leads to the following pointwise convergences
	\begin{equation*}
	\forall f \text{ Lipschiz,}\quad \forall y\in\S^2,  \quad\quad \frac{1}{n}\sum_i e^{-\frac{\|x_i-y\|^2}{4t}}\rightarrow   \int e^{-\frac{\|x-y\|^2}{4t}}d\mu(x) 
	\end{equation*}
    \begin{equation*}
    \forall f \text{ Lipschiz,}\quad \forall y\in\S^2,  \quad\quad \frac{1}{n}\sum_i e^{-\frac{||x_i-y||^2}{4t}}f(x_i)\rightarrow   \int e^{-\frac{\|x-y\|^2}{4t}}f(x)d\mu(x)        
    \end{equation*}
	Definitions \ref{eq:Heat Kernel Graph Laplacian operator} and \ref{eq:Functional approximation to the Laplace-Beltrami operator} end the proof.
\end{proof}

>>>>

We start by proving that for smooth functions, the sum converges toward an integral as the sampling increase in size.
\begin{prop}\label{prop:1}
	For an equal area sampling $\{x_i\in\S^2\}_{i=0}^{n-1}: A_i=A_j \forall i,j$ of the sphere it is true that for all $f: \S^2 \rightarrow \R$ Lipschitz with respect to the Euclidean distance $\|\cdot\|$ with Lipschitz constant $C_f$
	\begin{equation*}
	\left| \int_{\S^2}f({ x})\text{d}{\mu(x)} - \frac{1}{n}\sum_i f( x_i)\right|\leq C_f d^{(n)}.	    
	\end{equation*}
	Furthermore, for all $y\in\S^2$ the Heat Kernel Graph Laplacian operator $L^t_n$ converges pointwise to the functional approximation of the Laplace Beltrami operator $L^t$
	\begin{equation*}
	 L_n^tf(y)\xrightarrow{n\to\infty} L^tf(y).
	\end{equation*}
\end{prop}
\begin{proof}

	Assuming $f:\mathbb S^2 \rightarrow \R$ is Lipschitz with Lipschitz constant $C_f$, we have
	\begin{equation*}
	\left| \int_{\sigma_{i}}f({ x})\text{d}{\mu(x)} - \frac{1}{n}f( x_i)\right| \leq C_fd^{(n)}\frac{1}{n},	    
	\end{equation*}
	where $\sigma_i\subset \S^2$ is the subset of the sphere corresponding to the patch arround $x_i$. Remember that the sampling is equal area.
	Hence, using the triangular inequality and summing all the contributions of the $n$ patches, we obtain
	\begin{equation*}
	\left| \int_{\S^2}f({ x})\text{d}{\mu(x)} - \frac{1}{n}\sum_i f( x_i)\right| \leq \sum_i \left| \frac{1}{4\pi^2} \int_{\sigma_{i}}f({ x})\text{d}{\mu(x)} - \frac{1}{n}f( x_i)\right|\leq n  C_fd^{(n)}\frac{1}{n} = C_fd^{(n)}
	\end{equation*}
	A direct application of this result leads to the following pointwise convergences
	\begin{equation*}
	\forall f \text{ Lipschiz,}\quad \forall y\in\S^2,  \quad\quad \frac{1}{n}\sum_i e^{-\frac{\|x_i-y\|^2}{4t}}\rightarrow   \int e^{-\frac{\|x-y\|^2}{4t}}d\mu(x) 
	\end{equation*}
    \begin{equation*}
    \forall f \text{ Lipschiz,}\quad \forall y\in\S^2,  \quad\quad \frac{1}{n}\sum_i e^{-\frac{||x_i-y||^2}{4t}}f(x_i)\rightarrow   \int e^{-\frac{\|x-y\|^2}{4t}}f(x)d\mu(x)        
    \end{equation*}
	Definitions \ref{eq:Heat Kernel Graph Laplacian operator} and \ref{eq:Functional approximation to the Laplace-Beltrami operator} end the proof.
\end{proof}
